\Title

### 2021-07-14 manuscript/content.tex
Add a discussion section for the australia results
Move some of the text from the end of the results section here.

Finally, we proceeded to estimate the source coefficients using the entire
dataset and the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
observed data after each iteration of the algorithm.
The estimated source coefficients were then used to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated grid.
Grid points that are further than 50\km{} from the nearest data point are
masked to avoid unrealistic extrapolations.

The resulting grid preserves the high resolution of the original data while
avoiding aliasing artifacts due to the block averaging.
Some parts of the grid are smoother and with reduced amplitude (e.g., some
southwestern parts), which is expected from the upward continuation that was
performed to have the grid at a constant height.
On a modest workstation with 16 cores and 16~Gigabytes of RAM,
estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
$\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.

Fig.~\ref{fig:australia-residuals} shows the difference between the observed
and predicted gravity disturbances.
The inset figure shows a histogram of these residuals, which are approximately
normally distributed around zero.
The largest residuals are located in regions with high-amplitude
short-wavelength features in the observed data.

@@

>>>>

Finally, we proceeded to estimate the source coefficients using the entire
dataset and the parameters previously determined.
The estimated source coefficients were then used to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
On a modest workstation with 16 cores and 16~Gigabytes of RAM,
estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
$\sim 1.3$~hours and the prediction step took $\sim 18$~minutes.

Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated grid.
Grid points that are further than 50\km{} from the nearest data point are
masked to avoid unrealistic extrapolations.
Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
observed data after each iteration of the algorithm.
Fig.~\ref{fig:australia-residuals} shows the difference between the observed
and predicted gravity disturbances.
The inset figure shows a histogram of these residuals, which are approximately
normally distributed around zero.

@@

\subsection{Australia gravity data}

The application of the gradient-boosted equivalent sources to the Australian
gravity dataset demonstrates that the method is able to interpolate and
upward-continue large datasets in a reasonable amount of time using only modest
computational resources.
The resulting grid (Fig.~\ref{fig:australia}) preserves the high resolution of
the original data while avoiding aliasing artifacts due to the block averaging
of the source locations.
Some parts of the grid are smoother and have lower amplitudes than the original
data (e.g., some southwestern parts), which is expected from the upward
continuation that was performed to have the grid at a constant height.

The largest residuals in Fig.~\ref{fig:australia-residuals} are located in
regions with high-amplitude short-wavelength features in the observed data.
This is expected since the method involves some degree of smoothing because of
the use of damping and the source depths.
There are also low-amplitude long-wavelength residual signals that seem to
coincide with some of the windows of the gradient-boosting method.
A possible cause of these features is inability of the equivalent-sources
within a window to adequately fit the long-wavelength components of the data.
We note, however, that all of these long-wavelength residuals are smaller than
1 mGal in amplitude and do not represent a significant source of errors.
